BoostEM

### 2014-05-07 paper/paper.tex
blakhwf
soefkwelfjwe

\subsection{Methodology}
STEVE
\subsection{Results}
\section{Discussion}
STEVE 
\section{Conclusions}
%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

>>>>

\subsection{Methodology}
STEVE
\subsection{Results}

 \begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/accDrops.pdf}
\caption{Average decrease in 10 fold cross validation \% accuracy using ID3 from 20\% to 5\% of the data being labeled}
\label{accDrop}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/bankAcc.pdf}
\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
\label{bankAcc}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/parkAcc.pdf}
\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
\label{parkAcc}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/breaAcc.pdf}
\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
\label{breaAcc}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/vertAcc.pdf}
\caption{Average 10 fold cross validation \% accuracy using ID3 on Various algorithms, 20\% labeled data}
\label{vertAcc}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/bankAcc5.pdf}
\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
\label{vertAcc}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/breaAcc5.pdf}
\caption{Average 10 fold cross validation \% accuracy using Naive Bayes on Various algorithms, 5\% labeled data}
\label{vertAcc}
\end{figure}

\section{Discussion}
STEVE 
\section{Conclusions}
%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
